---
title: "Data Visualization"
author: "LEI SUN"
date: "2024-06-24"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE ,message=FALSE}
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/bad-drivers/bad-drivers.csv"
data <- read.csv(url)
```

# Visualization 1
Using the following graph, we can see that Hawaii, Pennsylvania, and Connecticut have the highest percentage of drivers involved in collisions due to speeding. Interesting!

```{r, echo = FALSE,message=FALSE}

library(ggplot2)
library(dplyr)

ggplot(data, aes(x = reorder(State, Percentage.Of.Drivers.Involved.In.Fatal.Collisions.Who.Were.Speeding), 
                 y = Percentage.Of.Drivers.Involved.In.Fatal.Collisions.Who.Were.Speeding)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +
  labs(title = "Percentage of Drivers Involved in Fatal Collisions - Speeding",
       x = "State",
       y = "Percentage of Drivers Involved in Fatal Collisions Due to Speeding") +
  theme_minimal()


```


# Visualization 2
The scatter plot shows the relationship between the percentage of drivers involved in fatal collisions who were speeding and those who were alcohol-impaired. Each point represents a state, and the plot helps to identify if there is any correlation between these two factors.


```{r, echo = FALSE,message=FALSE}

library(ggplot2)
library(dplyr)
ggplot(data, aes(x = Percentage.Of.Drivers.Involved.In.Fatal.Collisions.Who.Were.Speeding, 
                 y = Percentage.Of.Drivers.Involved.In.Fatal.Collisions.Who.Were.Alcohol.Impaired)) +
  geom_point(color = "darkred", alpha = 0.7) +
  labs(title = "Scatter Plot of Speeding vs. Alcohol-Impaired Drivers",
       x = "Percentage of Drivers Involved in Fatal Collisions Who Were Speeding",
       y = "Percentage of Drivers Involved in Fatal Collisions Who Were Alcohol-Impaired") +
  theme_minimal()
```